Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
yo nigger

\indent	The goal of this study is to compare the classification performance of the cognitive states associated with looking at a picture or looking at a sentence between subject. This objective introduces an important issue, namely, how the data from the fMRI scans can be compared between subjects. There are two mains ways this could be achieved. First, groups of voxels that are anatomically defined as belonging to a certain brain region, a region of interest (ROI), can be averaged into a single \emph{supervoxel}, which can be compared between subjects. Second, an anatomically defined talairach coordinate system can be used that maps the voxels of each subject onto an anatomically defined coordinate. The ROI averaging it is a rather crude method, and a lot of information of the individual voxels is lost, however, it also doubles as a dimensionality reduction method. By using the talairach coordinate system the data of each individual voxel can be used, however, to use this system the anatomical information for each subject has to be known and mapped onto the fMRI data in great detail. Because we lack the detailed data to precisely use the coordinate system we will use averaged ROI's in order to compare the classifiers.<insert citation in this paragraph> \\

@@

So how do we cope with this problem? On common solution is to reduce $|\vec{x}|$ by only using voxels belonging to a specific region of interest (ROI). However, this requires us to known which regions are actually of interest \textit{a priori}.
- ROIs, means, stddev, skew, kurtosis?

>>>>

       Insert alinea to explain shortly what our goal and used classifiers are (explained further in application?)\\

@@

To reducde the dimensionality of the input, two different methods are used.

ROI mapping. 
So how do we cope with this problem? On common solution is to reduce $|\vec{x}|$ by only using voxels belonging to a specific region of interest (ROI). However, this requires us to known which regions are actually of interest \textit{a priori}.
- ROIs, means, stddev, skew, kurtosis?

\subsection{Classifiers}
